### 2023-04-21 Documentation/UFMG/PFCII/Introduction/Introduction.tex
documentation

Electrohydrodynamic Atomization (EHDA) is a way to disintegrate a liquid into droplets by exposing it to a strong electric field.\cite{prunet}
The balance between capillary forces and the eletric field on the charged liquid defines the spraying dynamics and droplet size.
The electric current transported by the spray reveals characteristic shapes for different spray modes.
Signal processing techniques can allow a non-visual classification of the spray mode based on the electric current shape.\cite{Sjaaks}
The spray process imposes noise and random sequences on the measured signal making its classification not a trivial task. 
Industrial applications demand automated stabilization of a spray mode. 
This can be achieved by a closed-loop control system. 
This project is about to develop an application that can classify what dynamics the EHDA experiment is current in and control the variables to stabilize in the desired mode.

@@

This project aims to give continuity to the previous student work\cite{Monica}, 
Mônica, who foccused in detecting undesired discharges (sparks) in the system accusing high eletric potential. 
For that, she developed a python software routine to connect most of the peripherals and analysed the current data.
Her work corroborate the validation of this project motivating its development and optimization.

@@

\begin{enumerate}[a)]
\item multipurpose applications both scientific and industrial application.
\item Fully automated and intuitive system for EHDA research and industrial application.
\item Real Time non-visual classification of spraying modes.
\item Control and stabilization on a desired spraying mode.   
\item System Portability and versatility.
\end{enumerate}

\section{People envolved}
\label{sec:companies}

>>>>

Electrohydrodynamic Atomization (EHDA) is a way to disintegrate a liquid into droplets by exposing it to a strong electric field.\cite{prunet}
The balance between capillary forces and the electric field on the charged liquid defines the spraying dynamics and droplet size.
The electric current transported by the spray reveals characteristic shapes for different spray modes.
Signal processing techniques can allow a non-visual classification of the spray mode based on the electric current shape.\cite{Sjaaks}
The spray process imposes noise and random sequences on the measured signal making its classification not a trivial task. 
Industrial applications demand automated stabilization of a spray mode. 
This can be achieved by a closed-loop control system. 
This project is about to develop an application that can classify what dynamics the EHDA experiment is current in and control the variables to stabilize in the desired mode.

@@

This project aims to give continuity to the previous student work\cite{Monica}, 
Mônica, who focused in detecting undesired discharges (sparks) in the system accusing high electric potential. 
For that, she developed a python software routine to connect most of the peripherals and analyzed the current data.
Her work corroborates the validation of this project motivating its development and optimization.

@@

\begin{enumerate}[]
\item Multipurpose applications for both scientific and industrial approaches.
\item Fully automated and intuitive system for EHDA.
\item Real Time non-visual classification of spraying modes.
\item Control and stabilization on a desired dynamic. 
\item System portability and versatility.
\end{enumerate}

\section{People involved}
\label{sec:companies}

### 2023-04-21 Documentation/UFMG/PFCII/LiteratureReview/LiteratureReview.tex
documentation

The electrospraying of liquids herein is referred to as electrohydrodynamic atomization (EHDA). The atomization by primarily electrical (electro) forces of a liquid (hydro) that is moving (dynamic) during the atomization captures the essence of the phenomena.\cite{Grace}
That motion applies to the liquid certain velocity that is not enough to create the spray alone. Therefore, the eletric field itself is the responsible for the spraying dynamics.\cite{prunet}

@@

Dripping mode happens when the eletric field applied is not enough to change the meniscus shape, phenomena called field enhanced dripping.
In that situation the liquid droplet has, in general, size bigger than the capillary and low frequency intervals between each drop.

@@

Intermittent mode is defined when the eletric field forces starts to have a considerable effect in the meniscus and droplet formation. 
In this mode the droplet size is smaller than the nozzle, phenomena called microdripping, and the dripping frequency increases with the increasing of the field applied.

>>>>

The electrospraying of liquids herein is referred to as electrohydrodynamic atomization (EHDA). The atomization by primarily electrical (electro) forces of a liquid (hydro) that is moving (dynamic) during the atomization captures the essence of the phenomena.\cite{Grace}
That motion applies to the liquid certain velocity that is not enough to create the spray alone. Therefore, the electric field itself is the responsible for the spraying dynamics.\cite{prunet}

@@

Dripping mode happens when the electric field applied is not enough to change the meniscus shape, phenomena called field enhanced dripping.
In that situation the liquid droplet has, in general, size bigger than the capillary and low frequency intervals between each drop.

@@

Intermittent mode is defined when the electric field forces starts to have a considerable effect in the meniscus and droplet formation. 
In this mode the droplet size is smaller than the nozzle, phenomena called microdripping, and the dripping frequency increases with the increasing of the field applied.

### 2023-04-21 Documentation/UFMG/PFCII/Results/Results.tex
documentation

\begin{figure}[H]
    \center
    \includegraphics[width=17cm]{Figuras/19:03/axs1.png}
    \caption{Printscreen of the window shows user interface during the experiment.
        We can see the image generated by the camera in the background.
        The routine code running in pycharm software on the right side.
        And also real time signal plottings of the current data on the left side.}
\end{figure}

\begin{figure}[H]
    \centering
    \resizebox{170mm}{!}{\includegraphics{Figuras/19:03/axs2.png}}
    \caption{Printscreen during an experiment. At this moment we are in Multi Jet spraying mode. At the left we can see the current signal has a smoth and constant curve. We can also see the automatic classification at the right side.}
    \label{fig:multi_class_exp}
\end{figure}

@@

The results of the classification using the statistical values are illustrated in figures \ref{fig:step_voltage}, \ref{fig:raw_data} and \ref{fig:class_step_data}.

\begin{figure}[H]
    \center
    \includegraphics[width=12cm]{Figuras/19:03/voltage_step.png}
    \caption{Input voltage step graph. The range is beetween 3K-10K Volts. Step size of 50V and steo time of 5 seconds.}
    \label{fig:step_voltage}
\end{figure}

@@

Notice that is even possible to a visual classification. The Dripping mode has a current mean of 0V. The Intermittent state has a high variation of values that can be seen by the thickness of the graph. The Cone jet is a thiner graph because the signal is more constant. The Multi Jet is the same as Cone jet graph but with a higher mean value than cone Jet.

\begin{figure}[H]
    \center
    \includegraphics[width=12cm]{Figuras/19:03/classified-data-example.png}
    \caption{The same graph as \ref{fig:raw_data} but after the classification procedure. The colours are green: Dripping, Blue: Intermittent, Red: Cone Jet, Purple: Multi Jet and Black: Undefined.}
    \label{fig:class_step_data}
\end{figure}

\section{Map Sequence}
\label{sec:map_results}

    \subsection{Manual experiments}

    For better understand the effects of both voltage and flowrate in the spraying dinamycs manual experiments were made.
    Also in order to find the stability region of cone jet mode for the liquid and setup used.

@@

    \subsection{Manual x Automatic Cone Jet stability island maps}

@@

        \begin{figure}[H]
            \center
            \includegraphics[width=10cm]{Figuras/report3/map-exp-26-01.png}
            \caption{ exp-26-01-23 }
        \end{figure}

@@

            \begin{figure}[H]
                \center
                \includegraphics[width=9cm]{Figuras/report3/manual-mapping.png}
                \caption{ exp-26-01 manual classification}
            \end{figure}

            \begin{figure}[H]
                \center
                \includegraphics[width=9cm]{Figuras/report3/map4-stabilityIsland.png}
                \caption{ exp-26-01 automatic classification}
            \end{figure}

@@

            \begin{figure}[H]
                \center
                \includegraphics[width=7cm]{Figuras/report4/map7-manual.png}
                \caption{ exp-26-01 manual classification}
            \end{figure}

            \begin{figure}[H]
                \center
                \includegraphics[width=9cm]{Figuras/report4/map7-automatic-line.png}
                \caption{ exp-26-01 automatic classification}
            \end{figure}

@@

        \subsection{Non-dimensional axis}

@@

        Flowrate perturbation robustness test

@@

        The fuzzy approach of controller was explored and simulated but not used in the final version of the project.
        This because for this fuzzy approach we need to have the input variables for the fuzzy machine to be fuzzified.
        Which means that to use a fuzzy logic in our controller loop the classification must be fuzzyfied and our classification algorithm was not developed in order to give a classification and its current membership function.

        For that, I tried to fuzzyfi the controller input by the data acquired in the step routine. With the data I mapped the area of each spraying mode according to its potential and fuzzyfied this as shown in the Figure X.

        \begin{multicols}{2}
            \begin{figure}[H]
                \centering
                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/fuzzyfy_input.png}}
                \caption{Fuzzyfication}
                \label{fig:fuzzy_input}
            \end{figure}

            \begin{figure}[H]
                \centering
                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/defuzzyfy.png}}
                \caption{Defuzzyfication}
                \label{fig:fuzzy_output}
            \end{figure}
        \end{multicols}

>>>>

In this chapter, we will present the results obtained from our project. Firstly, we will demonstrate how the automation routine enhanced the research experiments. Next, we will discuss the validation of the classification results. Finally, we will showcase the performance of the implemented controller algorithms.

\section{Automation routine}
\label{sec:automation_routine}

The automated experiment routine is capable of acquiring a significantly more precise and extensive amount of data than what can be achieved by a human. Most power supplies available in the market rely on manual potentiometer adjustment to select the set point, which results in imprecise potential selection by a person. Moreover, manual adjustment takes some time to achieve the desired voltage. By running a computer routine that automatically sends commands to the power supply, we can achieve faster and more reliable experiment data.
We can see in figures \ref{fig:multi_class_exp1} and \ref{fig:multi_class_exp} the visual interface that the operator have during an experiment. All the important data of EHDA experiments are showed in the same screen and referring to each 0.5 seconds sampling time.

\begin{figure}[H]
    \center
    \includegraphics[width=17cm]{Figuras/19:03/axs1.png}
    \caption{Print screen of the window shows user interface during the experiment.
        We can see the image generated by the camera in the background.
        The routine code running in pycharm software on the right side.
        And also real time signal plottings of the current data on the left side.}
        \label{fig:multi_class_exp1}
\end{figure}

\begin{figure}[H]
    \center
    {\includegraphics[width=17cm]{Figuras/19:03/axs2.png}}
    \caption{Print screen during an experiment. At this moment we are in Multi Jet spraying mode. At the left we can see the current signal has a smooth and constant curve. We can also see the automatic classification on the right side.}
    \label{fig:multi_class_exp}
\end{figure}

@@

\subsection{Step Sequence}
\label{subsec:step_results}

Our first classification results were made exploring just the voltage ranges. For that we tried to stabilize all the other parameters such as humidity, temperature and external noise.
First, we fixed a flow rate to 0.7 uL/min. and ran a step routine as defined in \ref{subsec:step_routine}. The figure \ref{fig:step_voltage} shows the step voltages during the experiment and figure \ref{fig:raw_data} illustrates the raw data acquired with it. In figure \ref{fig:class_step_data} we see the same experiment data classified by spraying mode and separated by color.

\begin{figure}[H]
    \center
    \includegraphics[width=12cm]{Figuras/19:03/voltage_step.png}
    \caption{Input voltage step graph. The range is between 3K-10K Volts. Step size of 50V and step time of 5 seconds.}
    \label{fig:step_voltage}
\end{figure}

@@

\begin{figure}[H]
    \center
    \includegraphics[width=12cm]{Figuras/19:03/classified-data-example.png}
    \caption{The same graph as \ref{fig:raw_data} but after the classification procedure. The colors are green: Dripping, Blue: Intermittent, Red: Cone Jet, Purple: Multi Jet and Black: Undefined.}
    \label{fig:class_step_data}
\end{figure}

The graph of voltage scan as showed in \ref{fig:raw_data} has a common shape for different liquids and parameters. After having familiarity with it is even possible to classify the spraying modes by visual analysis. For example: 
Dripping mode has a current mean of 0V. The Intermittent state has a high variation of values that can be seen by the thickness of the graph. The Cone jet is a thinner graph because the signal is more constant. The Multi Jet is the same as Cone jet graph but with a higher mean value than cone Jet. Corona sparks are not showed in the graph because the discharges has a high current value and will be above the axis limits.

\subsection{Map Sequence}
\label{subsec:map_results}

For validation purposes and also to expose the benefits of the automated routine and classification

    For better understand the effects of both voltage and flow rate in the spraying dynamics manual experiments were made.
    Also in order to find the stability region of cone jet mode for the liquid and setup used.

@@

@@

@@

        \begin{figure}[H]
            \center
            \includegraphics[width=8cm]{Figuras/report3/manual-mapping.png}
            \caption{ exp-26-01 manual classification}
        \end{figure}

        \begin{figure}[H]
            \center
            \includegraphics[width=9cm]{Figuras/report3/map-exp-26-01.png}
            \caption{ exp-26-01 automatic classification}
        \end{figure}

@@

        \begin{figure}[H]
            \center
            \includegraphics[width=8cm]{Figuras/april/map5.png}
            \caption{ exp-26-01 manual classification}
        \end{figure}

        \begin{figure}[H]
            \center
            \includegraphics[width=10cm]{Figuras/april/map2.png}
            \caption{ exp-26-01 automatic classification}
        \end{figure}

@@

    \subsubsection{Non-dimensional axis}

@@

        Flow rate perturbation robustness test

@@

        The fuzzy approach of controller was explored and simulated but not used in the final version of the project.
        This because for this fuzzy approach we need to have the input variables for the fuzzy machine to be fuzzyfied.
        Which means that to use a fuzzy logic in our controller loop the classification must be fuzzyfied and our classification algorithm was not developed in order to give a classification and its current membership function.

        For that, I tried to fuzzyfy the controller input by the data acquired in the step routine. With the data I mapped the area of each spraying mode according to its potential and fuzzyfied this as shown in the Figure X.

            \begin{figure}[H]
                \centering
                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/fuzzyfy_input.png}}
                \caption{Fuzzyfication}
                \label{fig:fuzzy_input}
            \end{figure}

            \begin{figure}[H]
                \centering
                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/defuzzyfy.png}}
                \caption{Defuzzyfication}
                \label{fig:fuzzy_output}
            \end{figure}

### 2023-04-21 Documentation/UFMG/relatorios/literature review/main.tex
documentation

Another project is the \emph{experimental investigation of scaling laws for electrospraying: dieletric constant effect}\cite*[]{Chen_Pui}.
Where the author study about the quemical properties of the liquid being sprayed that can actually interfere in the dynamics of the process. 
In the paper the author emphasised about the liquid dieletric constant. For us this paper is interesting because we can understand better which liquid
has a better margin of operation in cone jet mode for example. What is missing in his article is that it is not mentioning all the variables that can interfere in the 
electrospray dynamics, which would be important to know.

>>>>

Another project is the \emph{experimental investigation of scaling laws for electrospraying: dielectric constant effect}\cite*[]{Chen_Pui}.
Where the author study about the quemical properties of the liquid being sprayed that can actually interfere in the dynamics of the process. 
In the paper the author emphasised about the liquid dielectric constant. For us this paper is interesting because we can understand better which liquid
has a better margin of operation in cone jet mode for example. What is missing in his article is that it is not mentioning all the variables that can interfere in the 
electrospray dynamics, which would be important to know.
